Parameter Space Representation of Pareto Front to Explore Hardware-Software Dependencies

### 2014-10-29 concepts.tex
fixed deps descr

\begin{definition}[Parameter dependencies]
\defL{dependency}
Given a system $S$, application $b \in \mathcal{B}$ and two parameters
$p_x$ and $p_y$, $p_x$ is said to
be dependent on another parameter $p_y$ if the optimal value of $p_x$,
that is the $v_{x} \in V_x$ which optimizes the objectives of the
evaluation function $E$, is dependent upon the current value of $p_y$. 
\end{definition}

When a dependency is present any safe assumption about the ``meaning'' of
$p_x$ in order to intuitively choose an appropriate value that
optimizes objective could be misleading.  It should be also pointed
out that it's often very difficult to identify dependencies using
analytical techniques and often designers have to use different
strategies to deal with such complexity, as seen
in~\secR{Related-work}.

>>>>

\begin{definition}[Parameter dependency]
\defL{dependency}
Given a system $S$, application $b \in \mathcal{B}$ and two parameters
$p_x$ and $p_y$, $p_x$ is said to
be dependent on another parameter $p_y$ if the optimal value of $p_x$,
that is the $v_{x} \in V_x$ which optimizes the objectives of the
evaluation function $E$, is dependent upon the current value of $p_y$. 
\end{definition}

When a dependency is present between parameters, it could be
misleading to use assumption about the ``meaning'' of
parameters in order to intuitively choose an appropriate value that
optimizes objectives.  It should be also pointed
out that it's often very difficult to identify dependencies using
analytical techniques and often designers have to use different
strategies to deal with such complexity, as seen
in~\secR{Related-work}. In this work we will often refer to
hardware/sofware dependencies, denoting dependencies occourring
between parameters belonging to the hardware and software categories,
as defined in~\secR{designspace}.
